---
title: ""
output:
  pagedown::html_paged:
    self_contained: true
    number_sections: false
knit: pagedown::chrome_print
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  results = "asis"
)

required_packages <- c(
  "pagedown",
  "readxl",
  "dplyr",
  "stringr",
  "knitr",
  "glue",
  "tibble"
)

installed <- rownames(installed.packages())
missing <- setdiff(required_packages, installed)

if (length(missing) > 0) {
  install.packages(
    missing,
    repos = "https://cloud.r-project.org"
  )
}

library(pagedown)
library(readxl)
library(dplyr)
library(stringr)
library(knitr)
library(glue)
library(tibble)

# ------------------------------------------------------------
# Project paths
# ------------------------------------------------------------

# When this file is saved as cv/cv-academic.Rmd, knitting normally
# starts from the cv folder. This resolves the repository root.
root_dir <- normalizePath("..", winslash = "/", mustWork = TRUE)

data_path <- function(file) {
  file.path(root_dir, "source-data", file)
}

# ------------------------------------------------------------
# Helpers
# ------------------------------------------------------------

format_date <- function(x) {

  if (
    length(x) == 0 ||
    is.na(x) ||
    trimws(as.character(x)) == ""
  ) {
    return("")
  }

  if (inherits(x, "Date")) {
    return(format(x, "%Y-%b"))
  }

  if (inherits(x, c("POSIXct", "POSIXt"))) {
    return(format(as.Date(x), "%Y-%b"))
  }

  # Excel date serials
  if (is.numeric(x)) {

    # Preserve year-only numbers
    if (x >= 1900 && x <= 2200 && x == floor(x)) {
      return(as.character(as.integer(x)))
    }

    d <- as.Date(x, origin = "1899-12-30")
    return(format(d, "%Y-%b"))
  }

  x_chr <- trimws(as.character(x))

  # Already in desired format
  if (grepl("^\\d{4}-[A-Za-z]{3}$", x_chr)) {
    return(x_chr)
  }

  # Preserve year/range/Present entries
  if (
    grepl("^\\d{4}$", x_chr) ||
    grepl("^\\d{4}\\s*[-–]\\s*\\d{4}$", x_chr) ||
    grepl("^\\d{4}\\s*[-–]\\s*[Pp]resent$", x_chr)
  ) {
    return(x_chr)
  }

  formats <- c(
    "%Y-%m-%d",
    "%d/%m/%Y",
    "%d-%m-%Y",
    "%d-%b-%Y",
    "%d-%B-%Y",
    "%b-%Y",
    "%B-%Y",
    "%b %Y",
    "%B %Y",
    "%Y-%m"
  )

  for (fmt in formats) {

    d <- suppressWarnings(
      as.Date(x_chr, format = fmt)
    )

    if (!is.na(d)) {
      return(format(d, "%Y-%b"))
    }
  }

  x_chr
}


html_escape <- function(x) {
  x <- as.character(x)
  x <- gsub("&", "&amp;", x, fixed = TRUE)
  x <- gsub("<", "&lt;", x, fixed = TRUE)
  x <- gsub(">", "&gt;", x, fixed = TRUE)
  x
}


make_cv_table <- function(year, content) {

  tibble(
    year = year,
    content = content
  ) |>
    knitr::kable(
      format = "html",
      escape = FALSE,
      col.names = NULL,
      table.attr = 'class="cv-table"'
    )
}


# ------------------------------------------------------------
# Read Excel data
# ------------------------------------------------------------

grants <- read_excel(data_path("Grants.xlsx"))

seminars <- read_excel(data_path("Invited_Seminars.xlsx"))

outreach <- read_excel(data_path("Outreach.xlsx"))

presentations <- read_excel(data_path("Presentations.xlsx"))

science <- read_excel(data_path("Science_Communication.xlsx"))

service <- read_excel(data_path("Service_Roles.xlsx"))
```

<style>
:root {
  --last-updated: "\00a0 \00a0 Last updated: `r format(Sys.Date(), '%B %Y')`";
}

/* ============================================================
   PAGE
   ============================================================ */

@page {
  size: A4;
  margin: 10mm 10mm 12mm 10mm;

  @top-left {
    content: "Robin Rowland";
    font-family: Arial, Helvetica, sans-serif;
    font-size: 7.5pt;
    color: #777;
  }

  @top-right {
    content: var(--last-updated);
    font-family: Arial, Helvetica, sans-serif;
    font-size: 7.5pt;
    color: #777;
  }

  @bottom-right {
    content: counter(page);
    font-family: Arial, Helvetica, sans-serif;
    font-size: 7.5pt;
    color: #777;
  }
}

@page:first {
  @top-left {
    content: "";
  }

  @top-right {
    content: "";
  }
}

/* ============================================================
   BASE
   ============================================================ */

html,
body {
  font-family: Arial, Helvetica, sans-serif !important;
  font-size: 9pt !important;
  line-height: 1.22 !important;
  color: #111;
}

body {
  margin: 0 !important;
  padding: 0 !important;
}

p {
  margin: 0 0 2px 0 !important;
}

a {
  color: #236579;
  text-decoration: none;
}

strong {
  font-weight: 700;
}

.header-section-number {
  display: none !important;
}

/* ============================================================
   TITLE + CONTACT
   ============================================================ */

.title-and-contact {
  display: grid;
  grid-template-columns: 1fr auto;
  column-gap: 10mm;
  align-items: end;
  margin: 0 0 4mm 0;
}

.title-and-contact .title {
  margin: 0;
  padding: 0;
}

.title-and-contact h1.title {
  font-size: 20pt !important;
  line-height: 1 !important;
  font-weight: 700 !important;
  border: none !important;
  margin: 0 !important;
}

.contact-info {
  text-align: right;
  font-size: 8.7pt;
  line-height: 1.28;
  white-space: nowrap;
}

/* ============================================================
   PROFILE / KEY SKILLS
   ============================================================ */

.research-interests {
  display: grid;
  grid-template-columns: 27mm auto;
  column-gap: 3mm;
  margin-bottom: 1.5mm;
}

.research-interests .label {
  font-weight: 700;
}

.research-interests .interests {
  line-height: 1.3;
}

/* ============================================================
   SECTION HEADINGS
   ============================================================ */

h2 {
  font-size: 11pt !important;
  font-weight: 700 !important;
  line-height: 1.05 !important;
  margin: 4mm 0 1.2mm 0 !important;
  padding: 0 !important;

  border: none !important;
  border-top: none !important;
  border-bottom: none !important;

  break-after: avoid;
}

h3 {
  font-size: 9.5pt !important;
  font-weight: 700 !important;
  margin: 2.2mm 0 0.7mm 0 !important;
  border: none !important;
}

/* ============================================================
   CV TABLES
   ============================================================ */

.cv-entries {
  margin: 0 !important;
  padding: 0 !important;
}

.cv-table,
.cv-entries table {
  width: 100% !important;
  border-collapse: collapse !important;
  border-spacing: 0 !important;
  margin: 0 !important;
  padding: 0 !important;

  border: none !important;
  border-top: none !important;
  border-bottom: none !important;

  font-size: 9pt !important;
  line-height: 1.18 !important;
}

/* Remove all default pagedown / bootstrap table lines */
.cv-table thead,
.cv-table tbody,
.cv-table tr,
.cv-table th,
.cv-table td,
.cv-entries table thead,
.cv-entries table tbody,
.cv-entries table tr,
.cv-entries table th,
.cv-entries table td {
  border: none !important;
  outline: none !important;
  box-shadow: none !important;
}

/* Remove ALL alternating row shading */
.cv-table tr,
.cv-table tr:nth-child(odd),
.cv-table tr:nth-child(even),
.cv-table td,
.cv-table th,
.cv-entries table tr,
.cv-entries table tr:nth-child(odd),
.cv-entries table tr:nth-child(even),
.cv-entries table td,
.cv-entries table th {
  background: transparent !important;
  background-color: transparent !important;
}

.cv-table td,
.cv-entries table td {
  vertical-align: top !important;
  padding: 0.4mm 0 0.5mm 0 !important;
}

.cv-table td:first-child,
.cv-entries table td:first-child {
  width: 27mm !important;
  min-width: 27mm !important;
  max-width: 27mm !important;
  padding-right: 3mm !important;
  white-space: nowrap;
  font-weight: 400;
}

.cv-entry-title {
  font-weight: 700;
}

.cv-secondary {
  display: block;
  margin-top: 0.15mm;
}

.cv-note {
  display: block;
  margin-top: 0.15mm;
  font-size: 8.5pt;
}

.thesis-title {
  font-style: italic;
}

/* ============================================================
   EXPERIENCE
   ============================================================ */

.experience-block {
  margin: 0 0 1.5mm 0 !important;
  padding: 0 !important;
}

.experience-head {
  display: grid;
  grid-template-columns: 27mm auto;
  column-gap: 3mm;
  margin: 0 0 0.35mm 0;
  line-height: 1.16;
}

.experience-date {
  white-space: nowrap;
}

.experience-title {
  font-weight: 700;
}

.course-line {
  margin: 0.35mm 0 0.1mm 30mm;
  font-weight: 600;
}

/* ============================================================
   BULLETS
   ============================================================ */

ul {
  margin: 0.45mm 0 0.7mm 32mm !important;
  padding-left: 3.5mm !important;
}

li {
  margin: 0 0 0.25mm 0 !important;
  padding: 0 !important;
  line-height: 1.16 !important;
}

/* ============================================================
   PAGE BREAKS
   ============================================================ */

.pageBreak {
  break-after: page;
}

.keep-together {
  break-inside: avoid;
}
</style>

::: {.title-and-contact}

:::::: {.title}
<h1 class="title">Robin Rowland</h1>
::::::

:::::: {.contact-info}
**PhD Candidate | Wildlife Ecology**  \
[robinerowland@gmail.com](mailto:robinerowland@gmail.com) | 0421 902 622  \
Sippy Downs, QLD | University of the Sunshine Coast
::::::

:::

::: {.research-interests}

:::::: {.label}
**Profile**
::::::

:::::: {.interests}
Wildlife ecologist with demonstrated experience in data management, technical analysis and reporting, and stakeholder engagement across academic, government, and community partners. Skilled in maintaining large ecological datasets and communicating complex scientific information to diverse audiences. Proven project coordination and committee experience, with strong statistical analysis skills in R.
::::::

:::

::: {.research-interests}

:::::: {.label}
**Key skills**
::::::

:::::: {.interests}
Data management | Statistical analysis (R) | Project coordination | Stakeholder engagement | Scientific communication
::::::

:::

::: {.cv-entries}

## Education

```{r education}
education_year <- c(
  "2023–Present",
  "2012–2016"
)

education_content <- c(
  paste0(
    "<span class='cv-entry-title'>Doctor of Philosophy</span>",
    "<span class='cv-secondary'>University of the Sunshine Coast</span>",
    "<span class='cv-secondary'><em>Thesis: Impacts of Urban Living on Insectivorous Bats</em></span>",
    "<span class='cv-note'>Anticipated completion December 2026</span>"
  ),
  paste0(
    "<span class='cv-entry-title'>Bachelor of Arts (Honours Program), Animal Behaviour</span>",
    "<span class='cv-secondary'>Eckerd College, USA</span>"
  )
)

cat(
  make_cv_table(
    education_year,
    education_content
  )
)
```

## Relevant Experience

<div class="experience-block">

<div class="experience-head">
<div class="experience-date">2023-Feb–Present</div>
<div class="experience-title">PhD Researcher, University of the Sunshine Coast, QLD</div>
</div>

- Lead a research project examining the effects of urbanisation and roost environments on insectivorous bat health and physiology.
- Developed an open-access continental-scale database of Australian bat roost associations and a complementary functional-trait database.
- Work with private landholders, non-profit organisations, state and local government, and communicate findings to stakeholders.
- Mentor and assist with supervision and experimental design of six student research projects (three undergraduate, three honours).

</div>

<div class="experience-block">

<div class="experience-head">
<div class="experience-date">2024-Oct–Present</div>
<div class="experience-title">Bat Walk Workshop Leader, Moreton Bay Council, QLD</div>
</div>

- Organise and lead annual citizen science bat walks and public workshops.

</div>

<div class="experience-block">

<div class="experience-head">
<div class="experience-date">2024-Mar–Present</div>
<div class="experience-title">Student Scholar, GBatNet Global Union of Bat Diversity Networks</div>
</div>

- Participate in international working groups and meetings involving bat researchers, conservation practitioners and other specialists.
- Collaborate on a global review of Data Deficient bat species, including creation, cleaning and management of a large citation database.
- Contribute to development of globally relevant scientific communication guidelines as part of a Global Bat Communication Guidelines Working Group.

</div>

<div class="experience-block">

<div class="experience-head">
<div class="experience-date">2023-Mar–Present</div>
<div class="experience-title">Tutor, University of the Sunshine Coast, QLD</div>
</div>

<div class="course-line">ANM100 — Animal Ecology Field Course (×3)</div>

- Deliver course content on bat acoustics and provide support and instruction for first-year university students during field courses to North Stradbroke Island (Minjerribah).
- Demonstrate ecological field techniques including transects, acoustic monitoring and animal identification across diverse terrains.

<div class="course-line">ANM103 — Animal Form and Function (×3)</div>
<div class="course-line">ENS222 — Terrestrial Vertebrate Diversity & Ecology (×2)</div>

- Instruct university students in laboratory techniques and scientific writing, moderate student discussions and mark assignments.
- Lead student groups on annual vertebrate identification field trips.

</div>

<div class="experience-block">

<div class="experience-head">
<div class="experience-date">2017-Aug–2023-Feb</div>
<div class="experience-title">Outreach Coordinator, Tamborine Mountain Glow Worm Caves, QLD</div>
</div>

- Liaised with tour and school groups, production companies and news agencies to deliver tailored wildlife conservation information in a fast-paced environment.
- Represented the organisation at academic conferences and in communication with the public and scientific community through emails, reports and reviews.

</div>

<div class="experience-block">

<div class="experience-head">
<div class="experience-date">2019-Aug–2019-Nov</div>
<div class="experience-title">Volunteer, Southern Cross University Glider Program, Brisbane QLD</div>
</div>

- Captured, collected and recorded data from wild squirrel and sugar glider individuals.
- Installed and removed Elliott traps at study sites around the Brisbane area.

</div>

<div class="experience-block">

<div class="experience-head">
<div class="experience-date">2016-Jun–2016-Nov</div>
<div class="experience-title">Research Intern, Busch Gardens Animal Research Center, USA</div>
</div>

- Collected and analysed behavioural, physiological and parasite data on a range of mammalian and avian species.
- Coordinated with researchers to design novel experiments and deliver results from multiple parallel projects to internal and external stakeholders.

</div>

<div class="experience-block">

<div class="experience-head">
<div class="experience-date">2015-May–2015-Aug</div>
<div class="experience-title">Research Intern, Savannah State University Dolphin Science Lab, USA</div>
</div>

- Collected behavioural and environmental data on bottlenose dolphin individuals during weekly field surveys and assisted with database updates and maintenance.
- After the internship concluded, worked remotely with the lab to complete a study examining injury rates in local dolphin populations.

</div>

## Service Roles

```{r service-roles}
service_rows <- list()
i <- 1

while (i <= nrow(service)) {

  date_value <- service$Date[i]

  if (
    is.na(date_value) ||
    trimws(as.character(date_value)) == ""
  ) {
    i <- i + 1
    next
  }

  role_value <- html_escape(service$Role[i])
  display_date <- format_date(date_value)

  descriptions <- character()
  j <- i + 1

  while (
    j <= nrow(service) &&
    (
      is.na(service$Date[j]) ||
      trimws(as.character(service$Date[j])) == ""
    )
  ) {
    descriptions <- c(
      descriptions,
      html_escape(service$Role[j])
    )
    j <- j + 1
  }

  content <- paste0(
    "<span class='cv-entry-title'>",
    role_value,
    "</span>"
  )

  if (length(descriptions) > 0) {
    content <- paste0(
      content,
      "<span class='cv-secondary'>",
      paste(descriptions, collapse = "<br>"),
      "</span>"
    )
  }

  service_rows[[length(service_rows) + 1]] <- tibble(
    year = display_date,
    content = content
  )

  i <- j
}

service_df <- bind_rows(service_rows)

cat(
  make_cv_table(
    service_df$year,
    service_df$content
  )
)
```

## Grants and Awards

```{r grants}
grant_year <- vapply(
  grants$Date,
  format_date,
  character(1)
)

grant_content <- vapply(
  seq_len(nrow(grants)),
  function(i) {

    amount <- grants[["Amount (AUD)"]][i]

    if (!is.na(amount) && is.numeric(amount)) {
      amount <- format(
        amount,
        big.mark = ",",
        scientific = FALSE,
        trim = TRUE
      )
    }

    paste0(
      "<span class='cv-entry-title'>",
      html_escape(grants$Funder[i]),
      "</span>",
      "<span class='cv-secondary'>",
      "$", html_escape(amount), " AUD — ",
      html_escape(grants$Project[i]),
      " [", html_escape(grants$Role[i]), "]",
      "</span>"
    )
  },
  character(1)
)

cat(
  make_cv_table(
    grant_year,
    grant_content
  )
)
```

## Invited Seminars

```{r invited-seminars}
seminar_year <- vapply(
  seminars$Date,
  format_date,
  character(1)
)

seminar_content <- paste0(
  "<span class='cv-entry-title'>",
  html_escape(seminars[["Invited Seminars"]]),
  "</span>"
)

cat(
  make_cv_table(
    seminar_year,
    seminar_content
  )
)
```

## Presentations and Posters

```{r presentations}
presentation_year <- vapply(
  presentations$Date,
  format_date,
  character(1)
)

presentation_content <- paste0(
  "<span class='cv-entry-title'>",
  html_escape(presentations[["Talk Details"]]),
  "</span>"
)

cat(
  make_cv_table(
    presentation_year,
    presentation_content
  )
)
```

## Science Communication

```{r science-communication}
science_year <- vapply(
  science$Date,
  format_date,
  character(1)
)

science_content <- vapply(
  seq_len(nrow(science)),
  function(i) {

    talk <- html_escape(science$Talk[i])
    link <- science$Link[i]

    if (
      !is.na(link) &&
      nzchar(trimws(as.character(link)))
    ) {
      paste0(
        "<a href='",
        html_escape(link),
        "'><span class='cv-entry-title'>",
        talk,
        "</span></a>"
      )
    } else {
      paste0(
        "<span class='cv-entry-title'>",
        talk,
        "</span>"
      )
    }
  },
  character(1)
)

cat(
  make_cv_table(
    science_year,
    science_content
  )
)
```

## Outreach

```{r outreach}
outreach_year <- vapply(
  outreach$Date,
  format_date,
  character(1)
)

outreach_content <- paste0(
  "<span class='cv-entry-title'>",
  html_escape(outreach[["Talk Details"]]),
  "</span>"
)

cat(
  make_cv_table(
    outreach_year,
    outreach_content
  )
)
```

## Skills and Certifications

```{r skills}
skills_year <- rep("", 4)

skills_content <- c(
  "Statistical analysis in R — linear modelling, mixed modelling, and spatial modelling with temporal and spatial autocorrelation",
  "Operate and Maintain 4WD Vehicle (RIIVEH305F)",
  "Provide Advanced Resuscitation and Oxygen Therapy First Aid (HLTAID015)",
  "Provide Cardiopulmonary Resuscitation — CPR (HLTAID009)"
)

cat(
  make_cv_table(
    skills_year,
    skills_content
  )
)
```

## Referees

```{r referees}
ref_year <- c("", "")

ref_content <- c(
  paste0(
    "<span class='cv-entry-title'>Dr. Clare Stawski</span>",
    "<span class='cv-secondary'>Primary Supervisor — Senior Lecturer, University of the Sunshine Coast</span>",
    "<span class='cv-secondary'>cstawski@usc.edu.au — 07 5459 4761</span>"
  ),
  paste0(
    "<span class='cv-entry-title'>Dr. Alexis Levengood</span>",
    "<span class='cv-secondary'>Co-Supervisor and Field Course Leader — Research Fellow, University of the Sunshine Coast</span>",
    "<span class='cv-secondary'>alevengo@usc.edu.au — 04 5756 6657</span>"
  )
)

cat(
  make_cv_table(
    ref_year,
    ref_content
  )
)
```

:::
