---
output:
  pagedown::html_paged:
    number_sections: false
    css: ["academic_cv.css"]
links-to-footnotes: false
knit: pagedown::chrome_print
---

<!--
This CV template pulls SIX sections live from cv_data.xlsx (sheet "cv_entries"):
  Service Roles | Grants and Awards | Invited Seminars | Presentations and Posters |
  Science Communication | Outreach
To add/update an entry, edit cv_data.xlsx (see its "Instructions" and "Column guide"
sheets) and re-knit - no need to touch this file for those six sections.

Everything else (contact details, summary, education, experience, skills, referees)
is written directly below, since it changes rarely. Edit the text in place.

NOTE: this file assumes the following all live in the SAME flat folder as this
Rmd (no subfolders):
  - academic_cv.css
  - utility-functions.R  (for blank_year_when_repeated(), add_leading_zeroes_and_letter(), etc.)
  - cv_date_helpers.R    (shared date formatting used by the website and PDF)
  - cv_data.xlsx
from the template this was adapted from. If you reorganise into subfolders later,
update the css: and source() paths above to match.
-->

<style>
:root{
  --last-updated: "\00a0 \00a0 \00a0 \00a0 Last updated: `r format(Sys.Date(), '%B, %Y')`";
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(tidyverse)
library(knitr)
library(glue)
library(fontawesome)
library(readxl)
source("utility-functions.R")
source("cv_date_helpers.R")

cv_entries <- read_excel(
  "cv_data.xlsx",
  sheet = "cv_entries",
  # Preserve year-only versus month-year precision from Excel.
  col_types = c("guess", "text", "text", rep("guess", 9))
) |>
  mutate(
    # Keep exactly the useful precision from the spreadsheet:
    # 2026 -> 2026; Apr-2026 -> Apr-2026; 28-Apr-2026 -> Apr-2026.
    year = format_cv_date_range(date, date_end),
    date_sort = cv_date_sort(date)
  )
```

::: {.title-and-contact}

:::::: {.title}
<h1 class="title">Robin Rowland</h1>
::::::

:::::: {.contact-info}
PhD Candidate  \
robinerowland6143@gmail.com  \
Sippy Downs, QLD  \
[LinkedIn](#) <https://www.linkedin.com/in/robin-rowland-3b16a3152/>
::::::

:::

## Key skills
::: {.research-interests}

:::::: {.spacer}
::::::

:::::: {.interests}
Data management &bull; Statistical analysis (R) &bull; Project coordination &bull; Stakeholder engagement &bull; Scientific communication

Wildlife ecologist with demonstrated experience in data management, technical analysis and reporting, and stakeholder engagement across academic, government, and community partners. Skilled in maintaining large ecological datasets and communicating complex scientific information to diverse audiences. Proven project coordination and committee experience, and strong statistical analysis skills in R.
::::::
:::

::: {.cv-entries}
## Education
```{r}
tibble::tribble(
  ~year,           ~what,
  "2023 - present", "<span class='cv-entry-title'>Doctor of Philosophy</span>, University of the Sunshine Coast<br>Thesis: Impacts of Urban Living on Insectivorous Bats<br><span class='cv-entry-translation'>Anticipated completion: December 2026</span>",
  "2012 - 2016",     "<span class='cv-entry-title'>Bachelor of Arts (Honours Program), Animal Behaviour</span>, Eckerd College, USA"
) |>
  kable()
```

## Relevant experience
```{r}
tibble::tribble(
  ~year, ~what,

  "2023 --- present", "<span class='cv-entry-title'>PhD Researcher</span>, University of the Sunshine Coast, QLD<br>&bull; Lead a research project examining the effects of urbanisation and roost environments on insectivorous bat health and physiology<br>&bull; Developed an open-access continental-scale database of Australian bat roost associations and a complementary functional-trait database<br>&bull; Work with private landholders, non-profit organisations, and state and local government, and communicate findings to stakeholders<br>&bull; Mentor and assist with supervision and experimental design of six student research projects (three undergraduate, three honours)",

  "2024 --- present", "<span class='cv-entry-title'>Student Scholar</span>, GBatNet Global Union of Bat Diversity Networks<br>&bull; Participate in international working groups and meetings involving bat researchers, conservation practitioners, and other specialists<br>&bull; Collaborate on a global review of Data Deficient bat species, including the creation, cleaning, and management of a large citation database<br>&bull; Contribute to the development of globally relevant scientific communication guidelines as part of the Global Bat Communication Guidelines Working Group",

  "2023 --- present", "<span class='cv-entry-title'>Tutor</span>, University of the Sunshine Coast, QLD<br><span class='cv-entry-translation'>ANM100 --- Animal Ecology Field Course (&times;4)</span><br>&bull; Deliver course content on bat acoustics and provide support and instruction for first-year university students during a field course on North Stradbroke Island (Minjerribah)<br>&bull; Demonstrate ecological field techniques, including transects, acoustic monitoring, and animal identification, across diverse terrains and adapt delivery to varied student abilities<br><span class='cv-entry-translation'>ANM103 --- Animal Form and Function (&times;4) &nbsp;|&nbsp; ENS222 --- Terrestrial Vertebrate Diversity &amp; Ecology (&times;3)</span><br>&bull; Instruct university students in laboratory techniques and scientific writing, moderate discussions, and mark assignments within short turnaround periods<br>&bull; Lead student groups on annual vertebrate identification field trips",

  "2017 --- 2023", "<span class='cv-entry-title'>Outreach Coordinator</span>, Tamborine Mountain Glow Worm Caves, QLD<br>&bull; Liaised with tour and school groups, production companies, and news agencies to deliver tailored wildlife conservation information in a fast-paced environment<br>&bull; Represented the company at academic conferences and communicated with the public and scientific community through emails, reports, and reviews",

  "Aug 2019 --- Dec 2022", "<span class='cv-entry-title'>Literature Database Manager &amp; Website Editor</span>, Wildlife Tourism Australia<br>&bull; Sorted and standardised an existing literature database to improve accessibility, integrated an embedded Zotero library, and provided ongoing updates for new publications<br>&bull; Maintained and updated website content to reflect information and updates from individual member sites",

  "2016", "<span class='cv-entry-title'>Research Intern</span>, Busch Gardens Animal Research Center, USA<br>&bull; Collected and analysed behavioural, physiological, and parasite data on a range of mammalian and avian species<br>&bull; Coordinated with other researchers to design novel experiments and deliver results from multiple parallel projects to internal and external stakeholders",

  "2015", "<span class='cv-entry-title'>Research Intern</span>, Savannah State University Dolphin Science Lab, USA<br>&bull; Collected behavioural and environmental data on bottlenose dolphin individuals during weekly field surveys and assisted with database updates and maintenance<br>&bull; After the internship concluded, worked remotely with the laboratory to complete a study examining injury rates in local dolphin populations"
) |>
  kable()
```

## Service roles
```{r}
cv_entries |>
  filter(type == 'service', is.na(exclude)) |>
  mutate(where = if_else(!is.na(url), glue("[{where}]({url})"), where)) |>
  mutate(what = glue("<span class='cv-entry-title'>{what}</span>, {where}")) |>
  arrange(desc(date_sort)) |>
  select(year, what) |>
  kable()
```

## Grants and awards
```{r}
cv_entries |>
  filter(type == 'grants', is.na(exclude)) |>
  mutate(what = if_else(is.na(amount),
                        glue("<span class='cv-entry-title'>{what}</span>, {where}"),
                        glue("<span class='cv-entry-title'>{what}</span> ({amount}), {where}"))) |>
  mutate(what = if_else(is.na(additional_info), what, glue("{what}<br>{additional_info}"))) |>
  arrange(desc(date_sort)) |>
  select(year, what) |>
  kable()
```

## Invited seminars
```{r}
cv_entries |>
  filter(type == 'seminars', is.na(exclude)) |>
  mutate(host = case_when(
    !is.na(institution) & !is.na(department) ~ glue("{institution}, {department}"),
    !is.na(institution) ~ institution,
    TRUE ~ where
  )) |>
  mutate(what = glue("<span class='cv-entry-title'>{host}</span><br>{what}")) |>
  arrange(desc(date_sort)) |>
  select(year, what) |>
  kable()
```

## Presentations and posters
```{r}
cv_entries |>
  filter(type == 'presentations', is.na(exclude)) |>
  mutate(format_label = if_else(!is.na(format), glue("{format} --- "), "")) |>
  mutate(what = glue("<span class='cv-entry-title'>{what}</span><br>{format_label}{where}")) |>
  mutate(what = if_else(is.na(additional_info), what, glue("{what}, {additional_info}"))) |>
  arrange(desc(date_sort)) |>
  select(year, what) |>
  kable()
```

## Science communication
```{r}
cv_entries |>
  filter(type == 'sci_comm', is.na(exclude)) |>
  mutate(what = if_else(!is.na(url), glue("[{what}]({url})"), what)) |>
  mutate(what = glue("<span class='cv-entry-title'>{where}</span>, {what}")) |>
  arrange(desc(date_sort)) |>
  select(year, what) |>
  kable()
```

## Outreach
```{r}
cv_entries |>
  filter(type == 'outreach', is.na(exclude)) |>
  mutate(what = glue("<span class='cv-entry-title'>{what}</span>, {where}")) |>
  mutate(what = if_else(is.na(additional_info), what, glue("{what}<br>{additional_info}"))) |>
  arrange(desc(date_sort)) |>
  select(year, what) |>
  kable()
```

## Skills and certifications
```{r}
tibble::tribble(
  ~what,
  "Statistical analysis in R --- linear modelling, mixed modelling, and spatial modelling with temporal and spatial autocorrelation (UQ R Course)",
  "Operate and Maintain 4WD Vehicle (RIIVEH305F)",
  "Provide Advanced Resuscitation and Oxygen Therapy First Aid (HLTAID015)",
  "Provide Cardiopulmonary Resuscitation --- CPR (HLTAID009)"
) |>
  mutate(what = glue("&bull; {what}")) |>
  kable(col.names = NULL)
```

## Referees
```{r}
tibble::tribble(
  ~what,
  "<span class='cv-entry-title'>Dr Clare Stawski</span> (Primary Supervisor) --- Senior Lecturer, University of the Sunshine Coast<br>cstawski@usc.edu.au &nbsp;|&nbsp;",
  "<span class='cv-entry-title'>Dr Alexis Levengood</span> (Co-Supervisor and Field Course Leader) --- Research Fellow, University of the Sunshine Coast<br>alevengo@usc.edu.au &nbsp;|&nbsp;"
) |>
  kable(col.names = NULL)
```

:::
